Visualization and analysis of probability distributions of large temporal data

### 2022-02-17 report/response.Rmd

I appreciate all the comments and suggestions, and will incorporate them into future work. Specific comments are addressed as follows:

## Chapter 1

Perhaps though, this would be a good place to detail the co-authorship arrangements for the succeeding chapters, and for the student’s contribution to be stated clearly.

Done.
A table outlining the main chapters’ co-authorship arrangements included in Introduction.

@@

> Q14. Why do you chose to summarize 4 and 5 clusters from JS-NQT when sindex suggests 3 clusters?

Done.
The caption and description of the figure in the text have been changed to indicate that Fig. 4.9 depicts a visual summary of why three clusters are insufficient for this data set, however it is recommended by sindex summary plots. In a cluster analysis, it is standard practice to test a few cluster sizes before and after the optimal $k$ to see if a different number of clusters is useful. In this example, increasing the number of clusters actually unfolds some behavior which was not apparent with $k=3$ as suggested by sindex.

> Q15. The reference to the stationarity assumption in the Discussion needs clarification.

Done.
Clarification: "we have assumed the time series to be stationary" has been changed to "the conditional distributions are assumed to remain constant for the observation period" in the Discussion section.

### 2022-02-17 Rmd/01-intro.Rmd
Ch1 Q1 Catherine

The thesis is structured as follows. Chapter \@ref(ch-gravitas) provides details of the cyclic granularities, different classes, and computation, and also its usage in exploratory time series analysis through applications. This is implemented in the R package `gravitas`. Chapter \@ref(ch-hakear) provides guidance on how to choose significant cyclic granularities, which are likely to have interesting patterns across its categories. This is available as the R package `hakear`. Chapter \@ref(ch-gracsr) provides methods to explore heterogeneity in repetitive behavior for multiple time series over multiple cyclic granularities. This is in the developing R package `gracsr`. Chapter \@ref(ch-conclusion) summarizes the software tools developed for the work, and discusses future plans.

>>>>

The thesis is structured as follows. Chapter \@ref(ch-gravitas) provides details of the cyclic granularities, different classes, and computation, and also its usage in exploratory time series analysis through applications. This is implemented in the R package `gravitas`. Chapter \@ref(ch-hakear) provides guidance on how to choose significant cyclic granularities, which are likely to have interesting patterns across its categories. This is available as the R package `hakear`. Chapter \@ref(ch-gracsr) provides methods to explore heterogeneity in repetitive behavior for multiple time series over multiple cyclic granularities. This is in the developing R package `gracsr`. Chapter \@ref(ch-conclusion) summarizes the software tools developed for the work, and discusses future plans. Table \ref{tab:contribution-outline} details the publications, including my and my fellow co-authors contributions.

\begin{table}
\centering\footnotesize\tabcolsep=0.12cm
\caption{Table outlining the main chapters' co-authorship arrangements.}
\label{tab:contribution-outline}
\begin{tabular}{|p{1cm}|p{2cm}|p{1.5cm}|p{3.5cm}|p{3.5cm}|p{1.5cm}|}
\hline
\RaggedRight\textbf{Thesis Chapter}  & \RaggedRight\textbf{Publication Title}  & \RaggedRight\textbf{Status (published, in press, accepted or returned for revision)}  & \RaggedRight\textbf{Nature and} {\%} \RaggedRight\textbf{of student contribution} & \RaggedRight\textbf{Co-author name(s) Nature and} {\%} \RaggedRight\textbf{of Co-author’s contribution} & \RaggedRight\textbf{Co-author(s), Monash student Y/N} \\ \hline
2 & Visualizing probability distributions across bivariate cyclic temporal granularities & Published & 70\%. Concept, methodology development, writing first draft and software development & (1) Rob J Hyndman, Concept, methodology and software development, writing 12\% (2) Dianne Cook, Concept, methodology and software development, writing 12\% (3) Antony Unwin, Concept and software development 6\% & \multicolumn{1}{c|}{N} \\
\hline
3 & Detecting distributional differences between temporal granularities
for exploratory time series analysis & Working Paper & 80\%. Concept, methodology development, writing first draft and software development & (1) Rob J Hyndman, Concept, methodology development and writing 10\% (2) Dianne Cook, Concept, methodology development and writing 10\%  & \multicolumn{1}{c|}{N} \\
\hline
4 & Clustering time series based on probability distributions across temporal granularities & To be submitted & 80\%. Concept, methodology development, writing first draft and software development & (1) Dianne Cook, Concept, methodology development and writing 15\% (2) Rob J Hyndman, Concept, methodology development and writing 5\% & \multicolumn{1}{c|}{N} \\
\hline
\end{tabular}
\end{table}
